---
title: "Review"
output: 
  html_notebook:
    toc: true
    toc_float:
      toc_collapsed: true
    toc_depth: 3
    number_sections: true
    theme: cerule
---



# Setup

We have two data sets for this week's lab. Both come from the Stat2Data package which provides a large number of high quality data sets.

- `Hawks`
- `HighPeaks`

Please remember, capitalization matters! These data sets are Capitalized AND use caps in the column names rather than underscores.

```{r setup, include=FALSE}
library(lubridate)
library(tidyverse)
library(Stat2Data)
data(Hawks)

Hawks <-
  Hawks %>%
  mutate(
    Date = ymd(paste(Year, Month, Day)),
    WeekDay = wday(Date, label = TRUE)
  ) %>%
  select(
    Year:Day,
    WeekDay,
    CaptureTime:Crop)
```

# Hawks

## Data

### Description:

Data for a samples of hawks from three different species

### Format:

A data frame with 908 observations on the following 19 variables.

- Month	9=September to 12=December
- Day	Date in the month
- Year	Year: 1992-2003
- CaptureTime	Time of capture (HH:MM)
- ReleaseTime	Time of release (HH:MM)
- BandNumber	ID band code
- Species	CH=Cooper's, RT=Red-tailed, SS=Sharp-Shinned
- Age	A=Adult or I=Immature
- Sex	F=Female or M=Male
- Wing	Length (in mm) of primary wing feather from tip to wrist it attaches to
- Weight	Body weight (in gm)
- Culmen	Length (in mm) of the upper bill from the tip to where it bumps - into the fleshy part of the bird
- Hallux	Length (in mm) of the killing talon
- Tail	Measurement (in mm) related to the length of the tail (invented at the MacBride Raptor Center)
- StandardTail	Standard measurement of tail length (in mm)
- Tarsus	Length of the basic foot bone (in mm)
- WingPitFat	Amount of fat in the wing pit
- KeelFat	Amount of fat on the breastbone (measured by feel
- Crop	Amount of material in the crop, coded from 1=full to 0=empty

### Details:

Students and faculty at Cornell College in Mount Vernon, Iowa, collected data over many years at the hawk blind at Lake MacBride near Iowa City, Iowa. The data set that we are analyzing here is a subset of the original data set, using only those species for which there were more than 10 observations. Data were collected on random samples of three different species of hawks: Red-tailed, Sharp-shinned, and Cooper's hawks.

### Source
Many thanks to the late Professor Bob Black at Cornell College for sharing these data with us.

## Task 01

- Question: How many rows of data are in Hawks? How many columns?
- Answer:
    - Rows: 
    - Columns: 

Helpful Hint: You don't have to actually write any code to answer this question. But, if you want, you can use the console.

## Task 02

- Question: Students at Cornell captured hawks from 1992 to 2003. What was their most successful single year?
- Answer: 

```{r}
## YOUR CODE HERE!

```

## Task 03

- Question: I've never caught a hawk, but I'm sure you can catch one on any day of the week. Across all the years, on which day of the week did students capture the fewest birds?
- Answer: 

```{r}
## YOUR CODE HERE!

```

## Task 04

- Question: Which breed of hawk has, according to this data, the longest average wing? And what is the average length of this species' wing?
- Answer: 

Helpful Hints:

- You can drop NA values.
- The acronyms are defined in the data dictionary above.
- Since the measurement was already take in millimeters, whole numbers are sufficient. You don't need include anything beyond the decimal.

```{r}
## YOUR CODE HERE!

```

## Task 05

- Question: Which breed of hawk has, according to this data, has the smallest variance in weight?
- Answer: 

Helpful Hints:

- You can drop NA values.
- Since the measurement is in grams, whole numbers are sufficient.

```{r}
## YOUR CODE HERE!

```


## Task 06

- Question: Which sex of Hawk is most common in this data?
- Answer: 

```{r}
## YOUR CODE HERE!

```

## Task 07

- Question: Would you use this data to estimate wing length by sex for these three hawks?
- Answer:

Helpful Info:
- https://sciencing.com/tell-male-female-hawks-apart-5968694.html
- Use the data, your skills (plotting, data transformation, etc.), and the link above to make and support your argument.
- Hint: There is no single right answer.

```{r}
## YOUR CODE HERE!

```

## Task 08

- Question: Can we predict the weight of a hawk using only the wing length? Create a linear model which predicts weight as a function of wing length and plot the relationship using ggplot. If you can, draw the model on your scatter plot. In canvas, upload your plot and tell me if you think this is a good model. Use values such as the Adjusted R-squared value and the model's p-value to support your answer.
- Answer:

```{r}
## YOUR CODE HERE!

```

## Task 09

- Question: In your plot above, you may have noticed three to four natural groups. Use ggplot to tell me which variable best explains these groups, Sex, Age, or Species.
- Answer:

Helpful Hint:

- I recommend using color or facet_wrap to figure this out.
- I wrote the first part of the plot for you.
```{r}
## This code works, but it is incomplete.
## To complete this task, you must add something to it
## and figure out which variable is best explains the three groups.
ggplot(Hawks, aes(x = Wing, y = Weight)) +
  geom_point()
```

## Task 10

- Question: Draw a bar plot of the number of birds caught by Age and Species.
- Answer: Upload this plot to Canvas.

```{r}
## YOUR CODE HERE!

```
