---
title: "Review!"
format: html
---



# Goal

- Review & preparation for the midterm.
- There is no grade for this "assignment". I will not check it.
- Answers and example code can be found in practice-answers.qmd.
- This data, like our survey data, is about college students. But this time we have 100 rows rather than a little more than a dozen.
- I created hints.md to help you. It is full of hints!
- From the text:
    - [Data Import](https://r4ds.hadley.nz/data-import.html)
    - [Data Visualization](https://r4ds.hadley.nz/data-visualize.html)
    - [Data Transformation](https://r4ds.hadley.nz/data-transform.html)
    - [Exploratory Data Analysis](https://r4ds.hadley.nz/EDA.html)



# Setup

```{r setup, include=FALSE}
library(janitor)
library(tidyverse)
library(Stat2Data)

backpack <- Backpack |> clean_names() |> mutate(year = as.character(year))
rm(Backpack)
```



# Data

**Description:** Backpack weights for a sample of college students

**Format:** A data frame with 100 observations on the following 9 variables.

- backpack_weight: Backpack weight (in pounds)
- body_weight: Body weight (in pounds) 
- ratio: backpack_weight/body_weight 
- back_problems ‘0’=no or ‘1’=yes 
- major: Code for academic major 
- year: Year in school 
- sex: A factor with levels ‘Female’ ‘Male’ 
- status: Graduate or undergraduate? ‘G’ or ‘U’ 
- units: Number of credits taken that quarter 

**Details:** A survey of students at California Polytechnic State University (San Luis Obispo) collected data to investigate the question of whether back aches might be due to carrying heavy backpacks.

**Source:**

Imported from the Stat2Data package.

Mintz J., Mintz J., Moore K., and Schuh K., "Oh, My Aching Back! A
Statistical Analysis of Backpack Weights," Stats: The Magazine for
Students of Statistics, vol. 32, 2002, pp. 1719.



# Tasks


## Task 01: Average Backpack Weight

- **Question:** What is the average backpack weight in this sample?
- **Answer:** 
- Helpful Hints:
    - Remember that `mean()` must be used inside a `summarize()` function.
  
```{r}

## YOUR ANSWER HERE!!!

```


## Task 02: Min, Max, SD Backpack Weight

- **Question:** What is the minimum, maximum, and standard deviation of the backpack weight?
- **Answer:**
  - Min: 
  - Max: 
  - Standard Deviation: 
- Helpful Hints:
  - You can name the columns with an equal sign in `summarize()`.
  - It makes the results easier to read.
  - The unit should be in pounds (lbs).

```{r}

## YOUR ANSWER HERE!!!

```


## Task 03:

- **Question:** Is there a strong positive correlation body weight and the weight of the backpack carried?
- **Answer:** 
  
```{r}

## YOUR ANSWER HERE!!!

```


## Task 04: Draw a bar plot of student major:

- **Question:** Using a bar plot of student majors, which is the most common major in the sample?
- **Answer:** 
- Helpful Hints:
    - You don't have to put the major on the X axis. :-)
  
```{r}

## YOUR ANSWER HERE!!!

```


## Task 05: Do people with back problems carry heavier backpacks?

- **Question:** On average, do people with back problems carry heavier backpacks?
- **Answer:** 
- Helpful Hints:
    - You can group by a number column!
  
```{r}

## YOUR ANSWER HERE!!!

```


## Task 06: Which is the best predictor of carrying a heavy backpack?

- **Question:** Which factor is a better predictor of carrying a heavy backpack? Student sex or Student status (undergrad vs graduate student)? Use a box plot to answer this question and be prepared to upload both images to support you answer.
- **Answer:** 
- Helpful Hints:
    - The answer is either sex or status.
  
```{r}

## YOUR ANSWER HERE!!!

```

```{r}

## YOUR ANSWER HERE!!!

```


## Task 07:

- **Question:** On average, who is carrying more coursework (units), undergraduates or graduate students?
- **Answer:** 
- Helpful Hints:
    - You don't need a plot for this one.
    - Just tell me which group has the higher average amount of coursework.
  
```{r}

## YOUR ANSWER HERE!!!

```


## Task 08:

- **Question:** What percentage of our sample are undergrads?
- **Answer:** 
  
```{r}

## YOUR ANSWER HERE!!!

```


## Task 09: Density of backpack weight

- **Question:** Draw a density plot of backpack weight. Is backpack weight skewed and if yes, is it skewed positively or negatively.
- **Answer:** 
  
```{r}

## YOUR ANSWER HERE!!!

```


## Task 10: Box plot of body weight by year in school

- **Question:** Draw box plots of body weight by year in school. Based on this plot, does it appear that students get heavier the longer they stay in school?
- **Answer:** 
  
```{r}

## YOUR ANSWER HERE!!!

```


## Task 11: Percentage female biology majors

- **Question:** What percentage of Biology majors are Female?
- **Answer:** 
- Helpful Hints:
  - This time you really do have to calculate the percentage!!!
  
```{r}

## YOUR ANSWER HERE!!!

```


## Task 12: Percentage back problems by sex

- **Question:** Which sex has the highest percentage of back problems?
- **Answer:** 
  
```{r}

## YOUR ANSWER HERE!!!

```
